\section{English}
\subsection{Oral English}
\begin{itemize}
  \item I was like, "What?!" :someone) was like...口语中用于表达某人的一种反应，比如说的话或思想活动。
  \item That takes guts!：(something) takes guts 做某事需要勇气。Guts本意是内脏，引申为胆量。
  \item All right, so much for that one.：so much for (something) 人们放弃做一件事或努力泡汤的时候常说的话。
  \item We nailed it!:圆满完成某件事，或说得完全正确。Nail本意是钉钉子。
  \item I knew you'd give me a hard time about it!:give…a hard time about…跟某人过不去、嘲笑某人、难为某人。
  \item I might be 90 years old, but I'm still young at heart!:might… but… 也许……但是……，可以用来委婉地否定别人的观点。
  \item Just do it already!:Just… already!赶紧的做某事！这个短语一般都是在抱怨对方反应太慢，表现一种不耐烦的态度。
  \item Strangely enough, I just bought a bike.:strangely enough, …遇到巧合或惊讶的事时的表达，可以翻译为真巧、真稀奇。
  \item Could you give me a few pointers?:give someone pointers 给某人一些建议。Pointer指建议、提示、线索。
  \item Who are you to talk? You’re just as messy as me.:who... to talk?表示某人没有资格发表意见或批评别人，因为他/她自己也做得不够好。
  \item Is it just me, or is it hot in here?Is it just me, or…?这是一种委婉的抱怨，一般都是在看对方是否有同样的意见。
  \item Did I leave my book at your place, by any chance?:by any chance 口语中常用这一表达来询问是否有某种可能。
  \item The last thing I want is to hurt you.:The last thing I want is…我最不愿意做的事情就是……
  \item Don't get \textbf{all} impatient.all 在口语表达中，形容词前加一个all，可以增强感情色彩，通常是表达负面情绪。
  \item Summer will be over before you know it.:before you know it 表示事情过得非常快。
  \item I've never gotten into baseball for some reason.:get into something 对某事感兴趣。
  \item Man! You're on fire!:on fire 本意是着火了，引申意是指人的状态特别好。
  \item I find it hard to relate to him sometimes.:relate to someone/something理解、接受某人某事，与之有同感、有共鸣。
  \item You bet!:you bet 意思是“You can bet money on that”（你可以压钱赌一把），说明你完全同意对方的观点、提议等。
  \item Good thinking! That would be great.:good thinking 好主意，跟good idea同意。
  \item It's way past your bedtime!:way past Way相当于"far"，这个表达是远远超过某个点的意思。
  \item What? That's nuts!That's nuts! Nuts是非常口语化的表达，表示“crazy”疯了。
  \item My computer sucks! I need to get a new one.(something) sucks 在谈论糟糕的、让人失望的、不幸的事情时，人们常用这个表达。正式场合慎用。
  \item You know that guy you introduced me to at your party? What's his story?:What's (someone's) story?人们常用这一表达来询问不太熟悉的人的信息。相当于说， "Tell me more about that person"，再说说那人的情况吧。
  \item I didn't mean to walk in on you.:walk in on someone / something 走进一个地方打扰了里面的人或正在进行的事，通常是些尴尬的事……
  \item He's around fiftyish, I'd say.-ish 口语中，在一个词后面加-ish，就等于说"a little bit" ，"kind of"，给人一种大约的、模糊的、不确定的感觉。



\end{itemize}
